### 2016-04-29 ch01-intro/introduction.tex
More conclusion + small stuff everywhere
Some stuff, here and there

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}
  \section{System idenfication}

\begin{figure}

  \centering
  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
  \label{fig:intro:identification-cycle}
\end{figure}

   \section{Publications}
   The lion's share of this thesis has been published either in peer-reviewed scientific journals and conferences or has been submitted to such venues at the time of writing.
   This section links my different publications to the different sections in this thesis.
   For an overview of publications grouped by type, please refer to \pageref{publicationList}.

@@

The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and 
\begin{itemize}
  \item \fullcite{Geerardyn2014IFAC},
  \item \fullcite{Geerardyn2014ISMA}.
\end{itemize}
Preliminary results have been presented at local (non-refereed) conferences:
\begin{itemize}
  \item \fullcite{Geerardyn2013Benelux},
  \item \fullcite{Geerardyn2013ERNSI},
  \item \fullcite{Geerardyn2014Benelux},
  \item \fullcite{Geerardyn2014DYSCO}, and
  \item \fullcite{Geerardyn2014ERNSI}.
\end{itemize}
The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{SYSID}) and :
\begin{itemize}
  \item \fullcite{Voorhoeve2015SYSID}
  \item \fullcite{Voorhoeve2015ERNSI}
\end{itemize}

>>>>

\chapter{Introduction}
\def\thisDir{ch01-intro}
\tikzsetfigurename{ch01fig}
\myEpigraph{It's a dangerous business, Frodo, going out your door. You step onto the road, and if you don't keep your feet, there's no knowing where you might be swept off to.}{John Ronald Reuel Tolkien}{The Fellowship of the Ring}

In this chapter, we first discuss some basic aspects of system identification, some typical choices and how those relate to user-friendly system identification and this dissertation.

\section{System idenfication}
\subsection{Linear System theory}
\subsection{System Identification Approaches}

\subsubsection{White Box, Black Box or Grey Box}
\subsubsection{Time or Frequency Domain}
\subsubsection{Linear or nonlinear?}
\subsubsection{Time invariant or non?}

\section{User-friendly System Identification}
In this dissertation, we focus on developing system identification techniques that are `user-friendly'.
User-friendly should be understood as having a good user experience for two groups of users:
\begin{itemize}
  \item novice users, without formal training in system identification, optimization, \ldots and,
  \item well-seasoned identification practitioners that are already able to build good models.
\end{itemize}
Concretely, for novice users it is important to have straightforward techniques that require little interaction.
In practice, this boils down to methods that work well for a wide class of systems.
As such, only very generic assumptions of the system under test should be made and these should be easy to interpret.

\begin{figure}
  \centering
  \includegraphics[width=0.9\columnwidth]{\thisDir/figs/id-cycle.pdf}
  \caption[Identification loop]{Typical system identification loop. Figure based on \citep[Figure 1.10]{Ljung1999}.}
  \label{fig:intro:identification-cycle}
\end{figure}

\section{Publications}
   The lion's share of this thesis has been published in either peer-reviewed  journals or conferences.
   This section links my different publications to the different sections in this thesis.
   For an overview of publications grouped by type, please refer to page~\pageref{publicationList}.

@@

The use of the non-parametric \gls{FRF} estimation methods for \Hinf gain estimation (and in general the \gls{FRF} interpolation from \chapref{sec:hinf}) has been presented at the 2014 \gls{IFAC} World Conference in South Africa and 
\begin{itemize}
  \item \fullcite{Geerardyn2014IFAC},
  \item \fullcite{Geerardyn2014ISMA}.
\end{itemize}
Preliminary results have been presented at local (non-refereed) conferences:
\begin{itemize}
  \item \fullcite{Geerardyn2013Benelux},
  \item \fullcite{Geerardyn2013ERNSI},
  \item \fullcite{Geerardyn2014Benelux},
  \item \fullcite{Geerardyn2014DYSCO}, and
  \item \fullcite{Geerardyn2014ERNSI}.
\end{itemize}
The experimental work related to \chapref{sec:hinf} has also been presented at the 2015 \gls{IFAC} Symposium on System Identification (\textsc{sysid}) and :
\begin{itemize}
  \item \fullcite{Voorhoeve2015SYSID}
  \item \fullcite{Voorhoeve2015ERNSI}
\end{itemize}

### 2016-04-29 ch03-lrm/nonparametric.tex
Some stuff, here and there

\subsection{Local modeling}
Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
\begin{align}
  \true{G}(\omega_{k}+d) 
  &\approx
  \frac{\Sum_{i=0}^{\order{B}} b_i d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
    &\isdef
    \frac{\LocalModel[k]{B}(d)}%
           {\LocalModel[k]{A}(d)} 
           = \LocalModel[k]{G}(d)
  \text{,}
  \label{eq:LRM:model:G}
  \\
  \true{T}(\omega_k + d) &\approx
  \frac{\Sum_{i=0}^{\order{C}} c_i d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i d^i}
    &\isdef 
      \frac{\LocalModel[k]{C}(d)}%
           {\LocalModel[k]{A}(d)}
      = \LocalModel[k]{T}(d)
  \text{.}
  \label{eq:LRM:model:T}
\end{align}

@@

@@

\section{Derivation of the Bias of the \glsentrytext{LRM}}
\label{sec:biascalc}
Since the local design matrix \eqref{eq:nparam:designMatrix} of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.

@@

Do note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables~\citep{Hjorungnes2007,Hjorungnes2011}.
The derivatives are then computed with respect to these variables.

@@

\begin{figure}[htb]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-Inf.tikz}
  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is low enough for many practical uses. }
  \label{fig:nparam:comparison:noiseless}
\end{figure}

\paragraph{Good signal-to-noise ratios}
The next situation we consider is when $\SNR=60\unit{dB}$ as shown in \figref{fig:nparam:comparison:hiSNR}.
Here, the \gls{LPM} remains severly biased for small datasets ($\nBW < 12$).
However, for sufficiently long experiments ($\nBW > 32$), the bias becomes negligible.
For the \gls{LRM} and \gls{LRIC}, the bias is always much smaller than the variance.
In contrast to \gls{LPM}, the \gls{LPM} already reaches a constant variance level when $\nBW > 10$.
It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LPM} method.
It is hence not advantageous to use the \gls{LRIC} as-is.
For all methods (except the \gls{ETFE} and \gls{LRIC}), the simulations show that the \gls{RMSE} reaches
\begin{equation}
  \lim_{\nBW \to \infty} \RMSE \approx \frac{\SNR}{\Delta \SNR}
\end{equation}
where
\begin{equation}
  \Delta\SNR = \sqrt{\frac{\nth}{\nWind}}
\end{equation}
accounts for the smoothing action of local modeling (see \tabref{tbl:nparam:methods} for numerical values of $\Delta \SNR$).

@@

\begin{figure}[phtb]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\begin{figure}[phbt]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-40.tikz}
  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:midSNR}
\end{figure}

\paragraph{Poor signal-to-noise ratios}
In \figref{fig:nparam:comparison:lowSNR} and \figref{fig:nparam:comparison:terribleSNR}, the results are shown for $\SNR=20\unit{dB}$ and $\SNR=10\unit{dB}$ respectively.
Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
At $\SNR=20\unit{dB}$ the \gls{LPM} and the \gls{LRM} is significantly biased for small datasets ($\nBW < 6$), however, the \gls{LRM} still perform better than the \gls{LPM}.
For larger datasets ($\nBW \geq 16$), all methods perform similarly and at a nearly constant level of (variance) error.
The \gls{LRM}, in contrast to the \gls{LPM}, still contains an observable bias in the simulations.
At even lower $\SNR=10\unit{dB}$,  most methods perform quite poorly for short datasets ($\nBW < 6$).
However, here it can be seen that the $\lpm{7,4,4}$ outperforms both the $\lrm{7,1,1,1}$ and $\lrm{7,2,2,2}$ and slightly worse than $\lrm{6,2,2,2}$.
It can be seen that the bias error of the \gls{LPM} drops off more quickly ($\bigO{\nBW^{-3}}$) than the \gls{LRM} bias which drops in approximately $\bigO{\nBW^{-1}}$.

\begin{figure}[phtb]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-20.tikz}
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.
  The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}[phbt]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-10.tikz}
 \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}

\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
\end{guideline}

@@

>>>>

\subsection{Local modeling}
Local modeling methods  exploit the `smoothness' (or conversely `roughness') of the different terms of \eqref{eq:output-error-FD} over the frequency $\omega$.
In particular, we will assume that $U(\omega)$ is `rough' over the frequency~\citep{Schoukens2009LPM}, e.g. as is the case for noise excitations or random phase multisines (see further).
On the other hand, it is well-known that the transfer functions $\true{G}$, $\true{H}$ and hence also the corresponding transient contributions $T = T_G + T_H$ are smooth over the frequency.
As such, these smooth contributions can be approximated well around each frequency $\omega_k$ using a local rational model:
\begin{align}
  \true{G}(\omega_{k}+d) 
  &\approx
  \frac{\Sum_{i=0}^{\order{B}} b_i(k) d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
    &\isdef
    \frac{\LocalModel[k]{B}(d)}%
           {\LocalModel[k]{A}(d)} 
           = \LocalModel[k]{G}(d)
  \text{,}
  \label{eq:LRM:model:G}
  \\
  \true{T}(\omega_k + d) &\approx
  \frac{\Sum_{i=0}^{\order{C}} c_i(k) d^i}
            {1 + \Sum_{i=1}^{\order{A}} a_i(k) d^i}
    &\isdef 
      \frac{\LocalModel[k]{C}(d)}%
           {\LocalModel[k]{A}(d)}
      = \LocalModel[k]{T}(d)
  \text{.}
  \label{eq:LRM:model:T}
\end{align}

@@

\begin{remark}
It should be noted that \eqref{eq:LRM:model:G} and \eqref{eq:LRM:model:T} are essentially isomorphic to a continuous-time transfer function model with complex coefficients.
The discrete-time counterparts (i.e. substituting $d^i \to \exp (ji d \Ts)$ in the expressions), have been tried as well.
However, these preliminary experiments did not yield estimates that were numerically reliable.
\end{remark}

@@

\section{Derivation of the Bias of the \glsentrytext{LRM}}
\label{sec:biascalc}
Since the local design matrix $\LocalMatrix{K}$, see \eqref{eq:nparam:designMatrix}, of the \gls{LRM} contains the noisy output spectrum $\LocalVector{Y}$ when $\order{A} > 0$, the \gls{LRM} is expected to be a biased estimator.
In this section, we will derive expressions for the bias such that it can be quantified how important this bias is in different situations.

@@

Note that the estimated parameters $\theta \in \ComplexMatrix{\nth \times 1}$ but that $\ELSCost{\theta}$ is a real-valued function.
In contrast to a complex-valued function, this requires additional attention when the derivatives are calculated~\citep{Messerschmitt2006} and~\citep[Section 15.9]{Pintelon2012} since $\ELSCost{\theta}$ is not an analytic function.
Particularly, the function $\ELSCost{\theta}$ is regarded as a two-dimensional function $\ELSCost{\theta,\conj{\theta}}$ where $\conj{\theta}$ and $\theta$ are considered as independent variables~\citep{Hjorungnes2007,Hjorungnes2011}.
The derivatives are then computed with respect to these variables.

@@

\begin{figure}[htb]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-Inf.tikz}
  \caption[Comparison of local models for $\SNR = \infty$]{Local modeling of a discrete-time system results in an approximation error that is small enough for many practical uses. }
  \label{fig:nparam:comparison:noiseless}
\end{figure}

\paragraph{Good signal-to-noise ratios}
The next situation we consider is when $\SNR=60\unit{dB}$ as shown in \figref{fig:nparam:comparison:hiSNR}.
Here, the \gls{LPM} remains severly biased for small datasets ($\nBW < 12$).
However, for sufficiently long experiments ($\nBW > 32$), the bias becomes negligible.
For the \gls{LRM} and \gls{LRIC}, the bias is always much smaller than the variance.
In contrast to \gls{LPM}, the \gls{LPM} already reaches a constant variance level when $\nBW > 10$.
It should also be noted that for the \gls{LRIC}, the variance is almost $10\unit{dB}$ more than the corresponding \gls{LPM} method.
It is hence not advantageous to use the \gls{LRIC} as-is.
For all methods (except the \gls{ETFE} and \gls{LRIC}), the simulations show that the \gls{RMSE} reaches
\begin{equation}
  \lim_{\nBW \to \infty} \RMSE \approx \frac{\SNR}{\Delta \SNR}
\end{equation}
where
\begin{equation}
  \Delta\SNR \isdef \sqrt{\frac{\nth}{\nWind}}
  \label{eq:nparam:deltaSNR}
\end{equation}
accounts for the smoothing action of local modeling (see \tabref{tbl:nparam:methods} for numerical values of $\Delta \SNR$).

@@

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-60.tikz}
  \caption[Comparison of local models for $\SNR = 60 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=60\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:hiSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-40.tikz}
  \caption[Comparison of local models for $\SNR = 40 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=40\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:midSNR}
\end{figure}

\paragraph{Poor signal-to-noise ratios}
In \figref{fig:nparam:comparison:lowSNR} and \figref{fig:nparam:comparison:terribleSNR}, the results are shown for $\SNR=20\unit{dB}$ and $\SNR=10\unit{dB}$ respectively.
Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
However
At $\SNR=20\unit{dB}$ the \gls{LPM} and the \gls{LRM} is significantly biased for small datasets ($\nBW < 6$), however, the \gls{LRM} still perform better than the \gls{LPM}.
For larger datasets ($\nBW \geq 16$), all methods perform similarly and at a nearly constant level of (variance) error.
The \gls{LRM}, in contrast to the \gls{LPM}, still contains an observable bias in the simulations.
At even lower $\SNR=10\unit{dB}$,  most methods perform quite poorly for short datasets ($\nBW < 6$).
However, here it can be seen that the $\lpm{7,4,4}$ outperforms both the $\lrm{7,1,1,1}$ and $\lrm{7,2,2,2}$ and slightly worse than $\lrm{6,2,2,2}$.
It can be seen that the bias error of the \gls{LPM} drops off more quickly ($\bigO{\nBW^{-3}}$) than the \gls{LRM} bias which drops in approximately $\bigO{\nBW^{-1}}$.

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-20.tikz}
  \caption[Comparison of local models for $\SNR = 20 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=20\unit{dB}$.
  The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:lowSNR}
\end{figure}

\begin{figure}[p]
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR-10.tikz}
 \caption[Comparison of local models for $\SNR = 10 \unit{dB}$]{Comparison of bias and variance of local modeling for $\SNR=10\unit{dB}$. The shaded area denotes the noise floor.}
  \label{fig:nparam:comparison:terribleSNR}
\end{figure}

\subsection{Summary}
\TODO{discussie}

\begin{guideline}[Use the LRM for resonant systems when $\SNR > 10 \unit{dB}$]
For resonant systems, the \gls{LRM} offers better performance than \gls{LPM} when a good \gls{SNR} is obtained in the frequency domain.
When the \gls{SNR} is poor ($\leq 10\unit{dB}$), the \gls{LPM} may perform a bit better than \gls{LRM}.
The \gls{LRIC} is unsuitable due to a high variance, but has a much smaller bias error than the non-iterative solutions.
\end{guideline}

@@

\TODO{introduction}

### 2016-04-29 ch03-lrm/truncation.tex
Conclusions finished? + some minor stuff
Some stuff, here and there

% 1) cut into NS segments of minimally NM samples
% 2) assume last segment == noise
%    start from back
% 3) F-test on Var, Var==RMS if dc == 0 (i.e. noise)
%    H0: s²(1) =  s²(2)
%    H1: s²(1) >  s²(2)
%    alpha >> ==> beta <<
% 4) if H1 and RMS(signal)/RMS(noise) > f
%    robustness, SNR
%    select segment i
% 5) refine until wanted resolution is obtained

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is small, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \leq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom~\citep{EncyclopediaOfMathematics}.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. 
This is done by solving the following expression

\begin{align}\label{eq:expFit}
\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
\end{align}
for $\ln A$ and $a$ in a least squares sense.
This is a quadratic problem in the parameters and, thus, amount to a convex optimization problem that can be solved directly.
Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.

@@

In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
\begin{itemize}
\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.

\item the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.

@@

@@

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption{Exponential fit of the impulse response of a boxcar averager. $\truncTime \gg \Nbc$ shows that a sub-optimal truncation point is found.}
         \label{fig:nparam:trunc:boxcar:impresp}
\end{figure}

>>>>

% 1) cut into NS segments of minimally NM samples
% 2) assume last segment == noise
%    start from back
% 3) F-test on Var, Var==RMS if dc == 0 (i.e. noise)
%    H0: s²(1) =  s²(2)
%    H1: s²(1) >  s²(2)
%    alpha >> ==> beta <<
% 4) if H1 and RMS(signal)/RMS(noise) < f
%    robustness, SNR
%    select segment i
% 5) refine until wanted resolution is obtained

@@

  The $F$-test is suited to compare the variances of different segments $\segm{\hat{g}}{i}$ and $\segm{\hat{g}}{i-1}$ \citep{Parsons1974}, while accounting for the degrees of freedom in each segment.
  For zero-mean noise, these variances are the \gls{RMS} value of each noise segment.
  This has the advantage that a segment in which the impulse response still has a significant amplitude is likely to have a large \gls{RMS} value, which is more likely to be detected.
  Let $s^2(i)$ denote the mean square value of segment $\segm{\hat{g}}{i}$, \emph{viz}:
  \begin{equation}
    s^2(i) 
    \isdef \frac{1}{L_S} \sum_{j=1}^{L_S} \left(\segm{\hat{g}}{i}(j)\right)^2
    = \left( \rms{\hat{g}^{[i]}} \right)^2
           \text{.}
  \end{equation}
  Starting with the last segment ($i = N_S$), the following null hypothesis and the alternative hypothesis are formulated:
  \begin{align}
     \nullHypothesis &: s^2(i-1) = s^2(i)\\
     \altHypothesis    &: s^2(i-1) > s^2(i)
     \text{.}
  \end{align}
  As segment $\segm{\hat{g}}{i}$ has been tested and been classified as noise (or assumed to be noise if $i=N_S$), the null hypothesis effectively states that the segment $\segm{\hat{g}}{i-1}$ is also noise.
  The alternative case occurs when $\segm{\hat{g}}{i-1}$ has a significant change, which indicates the presence of the signal.
  Using the $F$-test on the \gls{RMS} values of the two segments with a high confidence level of $\alpha=0.999$ and the aforementioned hypotheses, we can determine whether $\segm{\hat{g}}{i-1}$ is likely to be part of the actual impulse response.
  In particular, the null hypothesis is rejected when the empirical $F$ statistic is high, i.e.
  \begin{equation}
    F \isdef \frac{s^2(i-1)}{s^2(i)} \geq \ICDF{\FDistribution} \left( \alpha; n_{i-1}, n_{i} \right)
  \end{equation}
  where $ \ICDF{\FDistribution}$ is the inverse \gls{CDF} of the \mbox{$F$-distribution} with $n_{i-1}$ and $n_{i}$ degrees of freedom~\citep{EncyclopediaOfMathematics}.
  In this case $n_{i-1}$ and $n_{i}$ are the respective number of samples in the $(i-1)^{\text{th}}$ and $i^{\text{th}}$ segment of the impulse response.

@@

\item Fit an exponential function $Ae^{at}$ approximating $\hat g(t)$, in $t_\mathrm{max}\in\mathbb{T}_\mathrm{max}$. 
This is done by solving the following expression
\begin{align}\label{eq:expFit}
\ln \left|\hat g(t)\right|\approx \ln A+at,\ \mathrm{with}\ t\in\mathbb{T}_\mathrm{max},
\end{align}
for $\ln A$ and $a$ in a least squares sense.
This is a quadratic problem in the parameters and, thus, amount to a convex optimization problem that can be solved directly.
Since  $\ln \left|\hat g(t)\right|$ decreases for an increasing $t$ in $\mathbb{T}_\mathrm{max}$ (by construction in equation \eqref{eq:TmaxDef}), the estimated $a$ from equation \eqref{eq:expFit} is always negative.

@@

In \figref{fig:nparam:trunc:LPMvsTRunc} one observes the following:
\begin{itemize}
\item a decrease of the variance on the truncated estimate of about $10 \unit{dB}$ compared to the non-truncated \gls{LPM}, is observed.
Note also that the improvement in variance is proportional to the measurement time, i.e.
\begin{equation}
  \frac{\sampleStd{\trunc}}{\sampleStd{\LPM}} \approx \sqrt{\frac{\truncTime}{\Tm}}
\end{equation}
where $\Tm$ is the total measurement time.
Equivalently, this means that for \glspl{FRF} estimated with a finer frequency resolution, are improved more by truncation than coarsely spaced \glspl{FRF}.

@@

\item the error on the truncated \gls{LPM} estimate is strongly correlated over the frequency. This must be taken into account when formulating a maximum likelihood parametric estimator of the system.
It is, however, advised to use the raw data instead of such smoothed \glspl{FRF} to estimate a parametric model such that no bias is introduced into the parametric estimate.
In \chapref{sec:initvals}, however, it will be shown that smoothed \glspl{FRF} can lead to improved starting values.

@@

\begin{figure}
   \centering
        \setlength\figurewidth{0.68\columnwidth}
        \setlength\figureheight{0.68\figurewidth}
        \input{\thisDir/figs/expFitBoxAverager.tikz}
         \caption[Exponential fit of boxcar averager]{Exponential fit of the impulse response of a boxcar averager. $\truncTime \gg \Nbc$ shows that a sub-optimal truncation point is found.}
         \label{fig:nparam:trunc:boxcar:impresp}
\end{figure}
